### 2023-10-18 chapters/introduction.tex
Fix fraction

Besides enabling the advancement of early society, these technologies also brought with them novel challenges. 
In a likely attempt to reduce the effort needed to do Sumerian mathematics, Kushim produced a clay tablet with a multiplication table including fractional representations of common numbers. Assumedly unbeknownst to Kushim, this tablet would also come to contain one of the world's first recorded examples of a mathematical error; the statement: $5 \times \dfrac{1/2} = 5$ \parencite{nissen_archaic_1993}. 
Later, in its list of Pythagorean triplets, the Plimpton 322 clay tablet (\cref{fig:plimpton_332}) also has several errors, presumably made by a novice in Babylonian mathematics \parencite{neugebauer_mathematical_1945,britton_plimpton_2011}. 
% Apart from such inherent limitations of the tools, inadequate human proficiency in their use was also a source of error. 
Besides these human errors, inherent limitations of the tools also posed problems. 
Babylonian mathematicians did not formalize the difference between rational and irrational numbers which lead to approximation errors. For instance, the common practice of approximating $\pi$ with 3 \parencite{georges_universal_2001}. 
% Easy to overlook, the challenges we face in adopting new technologies today are not new but have been faced by humans for thousands of years. Today, as in ancient times, it was important to understand the limitations of technology and the need for human expertise in its use.

>>>>

Besides enabling the advancement of early society, these technologies also brought with them novel challenges. 
In a likely attempt to reduce the effort needed to do Sumerian mathematics, Kushim produced a clay tablet with a multiplication table including fractional representations of common numbers. Assumedly unbeknownst to Kushim, this tablet would also come to contain one of the world's first recorded examples of a mathematical error; the statement: $5 \times \frac{1}{2} = 5$ \parencite{nissen_archaic_1993}. 
Later, in its list of Pythagorean triplets, the Plimpton 322 clay tablet (\cref{fig:plimpton_332}) also has several errors, presumably made by a novice in Babylonian mathematics \parencite{neugebauer_mathematical_1945,britton_plimpton_2011}. 
% Apart from such inherent limitations of the tools, inadequate human proficiency in their use was also a source of error. 
Besides these human errors, inherent limitations of the tools also posed problems. 
Babylonian mathematicians did not formalize the difference between rational and irrational numbers which lead to approximation errors. For instance, the common practice of approximating $\pi$ with 3 \parencite{georges_universal_2001}. 
% Easy to overlook, the challenges we face in adopting new technologies today are not new but have been faced by humans for thousands of years. Today, as in ancient times, it was important to understand the limitations of technology and the need for human expertise in its use.
